Structured Versus Decorated Cospans

### 2022-04-07 cospans_compositionality_3.tex
fixed more refs

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/04/03 - third version sent to Compositionality

@@

\bibitem{BungeFiore} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ 
Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163. \href{https://doi.org/10.1017/S0960129599003023}{https://doi.org/10.1017/S0960129599003023}.

@@

\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  \href{https://doi.org/10.48550/arXiv.1502.00872}{https://doi.org/10.48550/arXiv.1502.00872}.

@@

\bibitem{GP1} M.\ Grandis and R.\ Par\'e, Limits in double categories, \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{40} (1999), 162--220.

\bibitem{GP2} M.\ Grandis and R.\ Par\'e, Adjoints for double categories, 
 \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{45} (2004), 193--240.

@@

\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ }\textbf{7} (2000), 71--147.

@@

\bibitem{Shulman2010} M.\ Shulman, Constructing symmetric monoidal bicategories. 
\href{https://doi.org/10.48550/arXiv.1004.0993}{https://doi.org/10.48550/arXiv.1004.0993}.

\bibitem{Stay} M.\ Stay, Compact closed bicategories, \textsl{Theory Appl.\ Categ.\ }\textbf{31} (2016), 755--798.    \href{https://doi.org/10.48550/arXiv.1301.1053}{https://doi.org/10.48550/arXiv.1301.1053}.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/04/07 - preparing third version sent to Compositionality

@@

\bibitem{BungeFiore} M.\ Bunge and M.\ Fiore, Unique factorisation lifting functors and categories of linearly-controlled processes, \textsl{Math.\ 
Struct.\ Comput.\ Sci.\ } \textbf{10} (2000), 137--163. \hfill \break
\href{https://doi.org/10.1017/S0960129599003023}{https://doi.org/10.1017/S0960129599003023}.

@@

\bibitem{Fong} B.\ Fong, Decorated cospans, \emph{Theory Appl.\ Categ.} \textbf{30} (2015), 1096--1120.  \hfill \break 
\href{https://doi.org/10.48550/arXiv.1502.00872}{https://doi.org/10.48550/arXiv.1502.00872}.

@@

\bibitem{GP1} M.\ Grandis and R.\ Par\'e, Limits in double categories, \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{40} (1999), 162--220. \href{http://www.numdam.org/item/CTGDC_1999__40_3_162_0/}{http://www.numdam.org/item/CTGDC$\underline{\;}$1999$\underline{\;\;}$40$\underline{\;}$3$\underline{\;}$162$\underline{\;}$0/}

\bibitem{GP2} M.\ Grandis and R.\ Par\'e, Adjoints for double categories, 
 \textsl{Cah.\ Top.\ G\'eom.\ Diff.} \textbf{45} (2004), 193--240.
 \href{http://www.numdam.org/item/CTGDC_2004__45_3_193_0/}{http://www.numdam.org/item/CTGDC$\underline{\;}$2004$\underline{\;\;}$45$\underline{\;}$3$\underline{\;}$193$\underline{\;}$0/}

@@

\bibitem{McCrudden} P.\ McCrudden, Balanced coalgebroids, \textsl{Theory Appl.\ Categ.\ }\textbf{7} (2000), 71--147.  \hfill  \break
 \href{https://www.emis.de/journals/TAC/volumes/7/n6/7-06abs.html}{https://www.emis.de/journals/TAC/volumes/7/n6/7-06abs.html}

@@

\bibitem{Shulman2010} M.\ Shulman, Constructing symmetric monoidal bicategories. \hfill \break
\href{https://doi.org/10.48550/arXiv.1004.0993}{https://doi.org/10.48550/arXiv.1004.0993}.

\bibitem{Stay} M.\ Stay, Compact closed bicategories, \textsl{Theory Appl.\ Categ.\ }\textbf{31} (2016), 755--798.   \hfill \break \href{https://doi.org/10.48550/arXiv.1301.1053}{https://doi.org/10.48550/arXiv.1301.1053}.
